---
title: "Developing Data Product"
author: "William Tai"
date: "6/13/2020"
output: ioslides_presentation
fontsize: 9pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<style type="text/css">
body{ /* Normal */
font-size: 12px;
}

pre { /* Code block - determines code spacing between lines */
font-size: 12px;
}
</style>

## Objectives
<font size = "4">The objectives of the assignment are to:</font>

<font size = "3">1. Create a shiny application</font>
<font size = "2">

- Write and deploy a shiny application using R-studio

- The application includes a form of input, operation on the ui input in server.R, and displayed reactive output.

The link is provided here: https://github.com/LiamRan/DevelopingDataProducts </font>

<font size = "3">
2. Create a R presentation</font>
<font size = "2">

- Five slides to pitch were done in R-studio presenter

- The presentation is hosted on Rpubs

- Sample R codes are embedded on the presentation

The link is provided here: https://rpubs.com/LiamRan/627315 </font>

## mtcars: Motor Trend Car Road tests
<font size = "3">

R comes with several built-in data sets, which are generally used as demo data for using with R functions. The mtcars dataset is one of the most used R built-in data sets.

The data was extracted from the 1974 Motor Trend US magazine and comprises fuel consumption (miles per gallon) and 10 aspects (number of cylinders, displacement, horsepower, rear axle ratio, weight, 1/4 mile time, engine, transmission, number of forward gears, and number of carburetors) of automobile design and performance for 32 automobiles (1973–74 models).

The content of the data set which contains 32 observations and 11 variables is shown below.</font>
```{r, echo = TRUE}
head(mtcars)
```

## R Codes

<font size = "3">The sample R codes used by the shiny application are provided below.
```{r, message = FALSE, echo = TRUE, results = "hide", fig.show="hide"}
attach(mtcars)  # This attach function allows the access to variables of the mtcars dataset
summary(wt)     # Summary of the car weight (1000 lbs)
cor(mpg,wt)     # Correlation between fuel consumption and car weight
```

The scatterplot is used for quantitative variables (displacement, horsepower, rear axle ratio, weight, and 1/4 mile time)

```{r, message = FALSE, echo = TRUE, results = "hide", fig.show="hide"}
plot(mpg,wt)  # Plot of fuel consumption versus car weight
```

The boxplot is used for qualitiative variables (cylinders, engine, transmission, number of forward gears, and number of carburetors).

```{r, message = FALSE, echo = TRUE, results = "hide", fig.show="hide"}
boxplot(mpg~cyl,col= c("green", "blue", "red"))  # Box plot of fuel consumption versus number of cylinders
```
</font>

## Shiny Application

<font size = "3">The application is located here: https://liamran.shinyapps.io/Shiny/

Left Pane: This pane provides a list of car mileage variables to be picked as an input.</font>
<font size = "2">

- Quantitative variables: disp (displacement), hp (horsepower), rear axle ratio (drat), weight (wt), 1/4 mile time (qsec)

- Qualititative variables: cylinders (cyl), engine (vs), transmission (am), number of forward gears (gears), number of carburetors (carb)

<font size = "3">

Main Panel: This pane provides a list of output</font>

<font size = "2">

- Data: Displays all 32 observations of the dataset

- Summary: Provides five-summary statistics (minimum, first quartile, median, third quartile, and maximum)

- Correlation: Relationship between fuel consumption (mpg) and selected car mileage variable

- Plot: Scatterplot or boxplot of fuel consumption (mpg) versus selected car mileage variable

</font>